Restrictive Clearance Comparison

### 2024-04-04 data-raw/RestrictiveClearance_comparison.Rmd
Added restrictive and non-restrictive, constant kelim versions of 1-/2-compartment models

```{r running-invivoPKfit}
minimal_pk <- pk(data = cvt %>%
                   filter(analyte_dtxsid %in% "DTXSID0020442"),
                 mapping = ggplot2::aes(
                   Chemical = analyte_dtxsid,
                   Chemical_Name = analyte_name_original,
                   DTXSID = analyte_dtxsid,
                   CASRN = analyte_casrn,
                   Species = species,
                   Reference = document_id,
                   Media = conc_medium_normalized,
                   Route = administration_route_normalized,
                   Dose = dose_level_normalized,
                   Dose.Units = "mg/kg",
                   Subject_ID = subject_id,
                   Series_ID = series_id,
                   Study_ID = study_id,
                   ConcTime_ID = conc_time_id,
                   N_Subjects = n_subjects_in_series,
                   Weight = weight_kg,
                   Weight.Units = "kg",
                   Time = time_hr,
                   Time.Units = "hours",
                   Value = conc,
                   Value.Units = "mg/L",
                   Value_SD = conc_sd_normalized,
                   LOQ = loq
                 ))

new_pk <- minimal_pk +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE,
                      suppress.messages = FALSE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
new_pk <- do_data_info(new_pk)

rest_pk <- do_prefit(new_pk, restrictive_clearance = TRUE)
rest_pk <- do_fit(rest_pk, n_cores = 6) # Worked!

nonrest_pk <- do_prefit(new_pk, restrictive_clearance = FALSE)
nonrest_pk <- do_fit(nonrest_pk, n_cores = 6) # Worked!

old_pk <- do_prefit(new_pk, restrictive_clearance = NULL)
old_pk <- do_fit(old_pk, n_cores = 6)

# Unfortunately, it seems the optimizer fails 
# Need to investigate why!!
# Are the kelims calculated too far from those estimated from the data?

>>>>

```{r running-invivoPKfit}
minimal_pk <- pk(data = cvt %>%
                   filter(analyte_dtxsid %in% common_chems[1:8]),
                 mapping = ggplot2::aes(
                   Chemical = analyte_dtxsid,
                   Chemical_Name = analyte_name_original,
                   DTXSID = analyte_dtxsid,
                   CASRN = analyte_casrn,
                   Species = species,
                   Reference = document_id,
                   Media = conc_medium_normalized,
                   Route = administration_route_normalized,
                   Dose = dose_level_normalized,
                   Dose.Units = "mg/kg",
                   Subject_ID = subject_id,
                   Series_ID = series_id,
                   Study_ID = study_id,
                   ConcTime_ID = conc_time_id,
                   N_Subjects = n_subjects_in_series,
                   Weight = weight_kg,
                   Weight.Units = "kg",
                   Time = time_hr,
                   Time.Units = "hours",
                   Value = conc,
                   Value.Units = "mg/L",
                   Value_SD = conc_sd_normalized,
                   LOQ = loq
                 ))

new_pk <- minimal_pk +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE,
                      suppress.messages = FALSE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  stat_error_model(error_group = vars(Chemical, Species, Reference)) +
  stat_model(model = c("model_flat", "model_1comp",
                       "model_1comp_rest", "model_1comp_nonrest"))
new_pk <- do_data_info(new_pk)

new_pk <- do_prefit(new_pk)

new_pk$prefit$par_DF %>% View()

new_pk <- do_fit(new_pk) # For troubleshooting

new_pk <- do_fit(new_pk, n_cores = 6) 
# Multidplyr error because of forgotten browser() call within log_likelihood
new_pk$fit %>% unnest(fit) %>% View()

coef(new_pk) %>% View()
eval_tkstats(new_pk) %>% View()

AIC(new_pk) %>% filter(method %in% "L-BFGS-B") %>% arrange(Chemical, Species) %>%
  View()

pl <- plot(new_pk, use_scale_conc = TRUE, method = "L-BFGS-B", n_interp = 10)
